Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-04 manuscript-chicago.Rmd
Add page numbers for quotes
Small Chicago style edit
Edits to discussion

# Discussion
In the present study, we investigated the dynamics of real-world events and
online communication on Twitter in Syria during Arab Spring. CRQA methodology
allows us to model the relationship between sociolinguistic cohesion and
exogenous political events. This work stands alongside the model of
Palestinian-Israeli social media and events developed by Zeitzoff (2011), and
the role of peripheral participants in the Syrian Arab Spring movement by
Steinert-Threlkeld (2017). By introducing the CRQA and WCRQA methods, we
demonstrate how language and social mobilization interact with events along the
conflict-cooperation continuum in Syria. We have introduced a novel theoretical
framework of sociolinguistic cohesion which we operationalize using a weighted
measure of lexical relationships. We examined how social mobilization both
virtually and physically evolve over time in tandem. Using nonlinear dynamical
time series analyses, we investigated the theory that virtual mobilization is
increasingly reflective of real-world events during times of strife.

## Cross-Recurrence Quantification Analysis
### Syria as Target
The significant result of DET for social cohesion with all and negative events
supports our first hypothesis that event salience is coupled with online social
cohesion. The frequency of all and negative events are thus associated with
greater shared trajectories with social cohesion that would be expected by
chance. However, when we specifically target positive events, the connection to
social cohesion fades, providing further support for our second hypothesis.
Positive events may be less coupled to social cohesion than more salient
negative events during times of turmoil; by contrast, overall event frequency
and negative event frequency are coupled with Twitter social cohesion.

@@

While interesting, the underlying meaning or drivers of this change in results
requires further investigation that incorporates the actual content of the
tweets themselves. One possible reason (among many) may be that the finding was
spurious. The positive external events from Syria may have been self-serving,
aiming to prevent intervention by other countries or to cover up what was
happening internally. During these moments, the increased cohesion may reflect a
surge from the Syrian people trying to raise awareness of the situation or to
decry the Syrian government's attempts to improve their international standing.
In this case, the increased coupling of positive events would be coupled not
with shared positive affect in social media but instead to shared negative
affect in social media in response. However, we cannot test this hypothesis with
the current data; future research should explore the semantic content of this
tweet corpus to determine the nature of the socially cohered language.

@@

# References

>>>>

# Discussion
In the present study, we investigated the dynamics of real-world events and
online communication on Twitter in Syria during Arab Spring. CRQA methodology
allows us to disentangle the relationship between sociolinguistic cohesion and
exogenous political events. This work stands alongside the model of
Palestinian-Israeli social media and events developed by Zeitzoff (2011), and
the role of peripheral participants in the Syrian Arab Spring movement by
Steinert-Threlkeld (2017). By introducing the CRQA and WCRQA methods, we
demonstrate how language and social mobilization interact with events along the
conflict-cooperation continuum in Syria. We have introduced a novel theoretical
framework of sociolinguistic cohesion which we operationalize using a weighted
measure of lexical relationships. We examined how virtual and physical social
mobilization evolve over time in tandem. Using nonlinear dynamical time series
analyses, we investigated the theory that virtual mobilization is increasingly
reflective of real-world events during times of strife.

## Cross-Recurrence Quantification Analysis
### Syria as Target
The significant result of DET for social cohesion with all and negative events
supports our first hypothesis that event salience is coupled with online social
cohesion. The frequency of all and negative events are thus associated with
greater shared trajectories with social cohesion than would be expected by
chance. However, when we specifically target positive events, the connection to
social cohesion fades, providing further support for our second hypothesis.
Positive events may be less coupled to social cohesion than more salient
negative events during times of turmoil; by contrast, overall event frequency
and negative event frequency are coupled with Twitter social cohesion.

@@

While interesting, the underlying meaning or drivers of this change in results
requires further investigation that incorporates the actual content of the
tweets themselves. One possible reason (among many) may be that the finding was
spurious. The positive external events from Syria may have been self-serving,
aiming to prevent intervention by other countries or to cover up what was
happening internally. During these moments, the increased cohesion may reflect a
surge from the Syrian people trying to raise awareness of the situation or to
decry the Syrian government's attempts to improve their international standing.
In this case, the increased coupling of positive events would be coupled not
with shared positive affect in social media but instead to shared negative
affect in social media in response. However, we cannot test this hypothesis with
the current time series data; future research should explore the semantic
content of this tweet corpus to determine the nature of the socially cohered
language.

@@

# Bibliography
